Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
some removal/editing of figures for Meadow

\definecolor{myblue}{rgb}{0.2, 0.3, 1.0}
\newcommand{\bluett}[1]{\textcolor{myblue}{\texttt{#1}}}
\newenvironment{allbluett}{\begin{alltt}\color{myblue}}{\end{alltt}}

@@

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale 
for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs 
of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain 
environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe 
model, including the assumptions made in designing it, the types of the principal functions and a description of the DSL 
as an algebraic type, constructor by constructor. Section \ref{section:example-saving} presents an example of a larger 
Marlowe contract, for incentivised saving. Section \ref{section:example-escrow} revisits the escrow example, and shows 
how it is described using a combination of Marlowe and Haskell constructs: that is, we use Marlowe as an embedded DSL. 
Section \ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section 
\ref{section:next-steps} enumerates the next steps for the project.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.6\textwidth]{pix/context.png}
\caption{The context for the contract}
\label{fig:context}
\end{center}
\end{figure}

@@

@@

\section{Marlowe as a DSL embedded in Haskell}
\label{section:example-escrow}

@@

Blockly's editor allows the user to visualise and edit
smart-contracts as interlocking blocks that can be dragged and dropped
like pieces of a jigsaw puzzle (see Figure~\ref{fig:detail-of-block}).
Meadow also provides functionality to generate syntactically correct
and formatted code (that is displayed in the upper right corner of the application),
and to convert the code back to its block representation.

Additionally, Meadow allows the user to use Meadow's Fay embedding from within the browser (see 
Figure~\ref{fig:embedded-demo}). Meadow includes a pruned copy of the Fay compiler, bundled with its Prelude module, 
its foreign interface, and a module with the definitions of the Marlowe primitives and a function to pretty-print 
Marlowe contracts. This allows the user to compile and execute, inside the browser, Fay
code that generates and prints a Meadow contract. When the user opens the embedded editor, the current Marlowe contract 
is embedded into a template of a Fay program that prints it. The user is able to modify this code in the left 
panel of the editor and use the advanced functionalities provided by Fay like, for example, bindings, 
list-comprehensions, turing-complete functions definitions, etc.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of Meadow tool
simulating the incentivised deposit contract.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail1}\caption{\label{fig:detail-of-block}Detail of five interlocked 
blocks.}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/embedded.png}
\par\end{centering}
\caption{\label{fig:embedded-demo}Screenshot of Meadow's embedded Fay editor.}
\end{figure}

@@

Thanks to IOHK staff Manuel Chakravarty, Duncan Coutts, Bernardo David, Charles Hoskinson, Aggelos Kiayias, Darryl 
McAdams, Bruno Woltzenlogel Paleo, and Phil Wadler for their collaboration, and to colleagues from the Universities of 
Kent and Leicester for their comments on previous presentations of this work.

>>>>

\definecolor{myblue}{rgb}{0.2, 0.3, 1.0}
\newcommand{\bluett}[1]{\textcolor{myblue}{\texttt{#1}}}
\newenvironment{allbluett}{\begin{alltt}\color{myblue}}{\end{alltt}}
\newcommand{\ignore}[1]{} % for commenting out large portions, surround by \ignore{ and }

@@

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale 
for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs 
of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain 
environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe 
model, including the assumptions made in designing it, the types of the principal functions and a description of the DSL 
as an algebraic type, constructor by constructor. 
%Section \ref{section:example-saving} presents an example of a larger Marlowe contract, for incentivised saving. 
Section \ref{section:example-escrow} revisits the escrow example, and shows 
how it is described using a combination of Marlowe and Haskell constructs: that is, we use Marlowe as an embedded DSL. 
Section \ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section 
\ref{section:next-steps} enumerates the next steps for the project.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.6\textwidth]{pix/context.png}
\caption{The context for a contract}
\label{fig:context}
\end{center}
\end{figure}

@@

\ignore{ % begin ignore

@@

} % end ignore

\section{Marlowe as an embedded DSL in Haskell}
\label{section:example-escrow}

@@

Blockly's editor allows the user to visualise and edit
smart-contracts as interlocking blocks that can be dragged and dropped
like pieces of a jigsaw puzzle. % (see Figure~\ref{fig:detail-of-block}).
Meadow also provides functionality to generate syntactically correct
and formatted code (that is displayed in the upper right corner of the application),
and to convert the code back to its block representation.

Additionally, Meadow allows the user to use Meadow's Fay embedding from within the browser. % (see Figure~\ref{fig:embedded-demo}). 
Meadow includes a pruned copy of the Fay compiler, bundled with its Prelude module, 
its foreign interface, and a module with the definitions of the Marlowe primitives and a function to pretty-print 
Marlowe contracts. This allows the user to compile and execute, inside the browser, Fay
code that generates and prints a Meadow contract. When the user opens the embedded editor, the current Marlowe contract 
is embedded into a template of a Fay program that prints it. The user is able to modify this code in the left 
panel of the editor and use the advanced functionalities provided by Fay like, for example, bindings, 
list-comprehensions, turing-complete functions definitions, etc.

@@

\begin{figure}[t]
\begin{centering}
\includegraphics[width=1.1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of Meadow tool
simulating the incentivised deposit contract.}
\end{figure}

%\begin{figure}
%\centering{}\includegraphics[scale=0.5]{pix/detail1}\caption{\label{fig:detail-of-block}Detail of five interlocked 
%blocks.}
%\end{figure}

@@

%\begin{figure}
%\begin{centering}
%\includegraphics[width=1\textwidth]{pix/embedded.png}
%\par\end{centering}
%\caption{\label{fig:embedded-demo}Screenshot of Meadow's embedded Fay editor.}
%\end{figure}

@@

Thanks to IOHK staff Manuel Chakravarty, Duncan Coutts, Bernardo David, Charles Hoskinson, Aggelos Kiayias, % Darryl McAdams, 
Bruno Woltzenlogel Paleo, Rebecca Valentine and Phil Wadler for their collaboration, and to colleagues from the Universities of 
Kent and Leicester for their comments on previous presentations of this work.
